Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2018-09-07 ms.tex
Some edits to charge trapping text.

The NP junction in Figure \ref{fig:npSchematic} is ``reverse-biased'' with a positive potential on the N-type material and negative potential on the P-type.
The positive potential on the N-type material attracts the negative charge carriers (electrons) whereas the negative potential on the P-type material attracts the  positve charge carriers (holes).
The reverse bias thus reduces the number of mobile charge carriers and increases the size of the depletion region.
The increased depletion region size also increases the well depth or capacity of electrons that the detector may collect before saturation.
The reverse bias is applied at each reset at the beginning of a detector's integration (\textbf{\textcolor{red}{Check!}}).
Figure \ref{fig:npSchematic} shows the case where the density of charge carriers is equal in the N-type and P-type semiconductors, but in reality, the density of the P-type semiconductor is much higher than the N-type, so the depletion region has a larger physical size on the N-type side.

Note that Figure \ref{fig:npSchematic} shows the mobile charge carriers only, so the depletion region, with no mobile charges is positively charged on the N-type side and negatively charged on the P-type side.
The undepleted region is electrically neutral because the nuclei of the N-type material have an equal number of extra protons as the negatively charged electrons.
Similarly, the undepleted region of the P-type semiconductor has fewer protons in its atomic nuclei producing an overall neutral charge \citep[e.g.][]{halliday2004physicsText}.
Textbook NP junction schematics often show the net charge and thus symbolize the regions with charge carriers as empty and the depletion region with ``+'' symbols on the N-type semiconductor and ``-'' symbols on the P-type˚.
The schematic in Figure \ref{fig:npSchematic} instead shows the mobile charge carriers as ``+'' and ``-'' because it is easier to understand the charge trapping effect \citep[e.g.][]{smith2008imgPersistence}.

When an incoming photon hits the (check if this wording is correct) n-type depletion region, it will excite an electron from the valence to conduction band which creates an electron-hole pair \citep{rieke2007irDetectorReview}.
The electron moves to the extremity of the depletion zone in the N-type material whereas the positive hole generated crosses the NP junction and adds a mobile charge to the P-type side.
The incoming photon has the effect of decreasing the size of the depletion region.
A second photon will excite another hole from the N-side that causes it to flow to the P side.
This continues and decreases the size of the depletion region.
The diffusion of charge carriers across the junction changes the voltage across the NP junction, which can be measured with a sensitive amplifier circuit.

@@

\subsection{Charge Trapping}
All HgCdTe detectors show a signal after bright illumination even if the illumination is removed; this is called persistence.
The mechanism that is proposed to explain persistence is that charges are trapped in the depletion region after illumination by photons as the detector well fills \citep{smith2008imgPersistence,leisenring2016persistence}.
After the reverse-bias voltage is applied (a reset) in an ideal detector, the depletion region will be devoid of mobile charge carriers (electrons and holes).
However, in real detectors, some charges are trapped within the depletion region.
During a future integration, these charges will be released and shrink the size of the depletion region, filling a pixel with spurious signal (Data Numbers) not related to that integration's illumination by photons.
This is visible after an illumination by a source, where a residual image of a bright star can appear in dark regions or dark frames following the illumination.

@@

>>>>

The NP junction in Figure \ref{fig:npSchematic} is ``reverse-biased'' with a positive potential on the N-type material and negative potential on the P-type.
The positive potential on the N-type material attracts the negative charge carriers (electrons) whereas the negative potential on the P-type material attracts the  positve charge carriers (holes).
The reverse bias thus reduces the number of mobile charge carriers and increases the size of the depletion region.
The increased depletion region size also increases the well depth or capacity of electrons that the detector may collect before saturation.
The reverse bias is applied at each reset at the beginning of a detector's integration.
Figure \ref{fig:npSchematic} shows the case where the density of charge carriers is equal in the N-type and P-type semiconductors, but in reality, the density of the P-type semiconductor is much higher than the N-type, so the depletion region has a larger physical size on the N-type side.

Note that Figure \ref{fig:npSchematic} shows the mobile charge carriers only, so the depletion region, with no mobile charges is positively charged on the N-type side and negatively charged on the P-type side.
The undepleted region is electrically neutral because the nuclei of the N-type material have an equal number of extra protons as the negatively charged electrons.
Similarly, the undepleted region of the P-type semiconductor has fewer protons in its atomic nuclei producing an overall neutral charge.
Textbook NP junction schematics often show the net charge and thus symbolize the regions with charge carriers as empty and the depletion region with ``+'' symbols on the N-type semiconductor and ``-'' symbols on the P-type˚ \citep[e.g.][]{halliday2004physicsText}.
The schematic in Figure \ref{fig:npSchematic} instead shows the mobile charge carriers as ``+'' and ``-'' because it is easier to understand the charge trapping effect this way \citep[e.g.][]{smith2008imgPersistence}.

When an incoming photon strikes the N-type depletion region, it will excite an electron from the valence to conduction band which creates an electron-hole pair \citep{rieke2007irDetectorReview}.
The electron moves to the extremity of the depletion zone in the N-type material whereas the positive hole generated crosses the NP junction and adds a mobile charge to the P-type side.
The incoming photon has the effect of decreasing the size of the depletion region.
A second photon will excite another electron-hole pair so that a hole moves to the P-type side.
This continues and decreases the size of the depletion region.
The diffusion of charge carriers across the junction changes the voltage across the NP junction, which can be measured with a sensitive amplifier circuit.

@@

@@

\subsection{Charge Trapping}
All HgCdTe detectors show a signal after bright illumination even if the illumination is removed; this is called persistence.
The physical mechanism that explain persistence is that charges are trapped in the depletion region after illumination by photons as the detector well fills \citep{smith2008imgPersistence,leisenring2016persistence}.
After the reverse-bias voltage is applied (a reset) in an ideal detector, the depletion region will be devoid of mobile charge carriers (electrons and holes).
However, in real detectors, some charges are trapped within the depletion region.
During a future integration, these charges will be released and shrink the size of the depletion region, filling a pixel with spurious signal (Data Numbers) not related to that integration's illumination by photons.
Figure \ref{fig:npSchematic} shows how the size of the depletion region changes after charges have been released, highlighted with red circles.
The persistence from trapped charge is visible after an illumination by a source, where a residual image of a bright star can appear in dark regions or dark frames following the illumination.
